### 2023-04-29 bachelorthesis/02-acknowledgement.tex
#39: Fixed Linebreak

First of all, I would like to express my greatest gratitude to my supervisor Arthur Peeters and Florian Rath. I would like to thank both of you for your guidance and support during the submission process of the briefcommunication and the helpful hands during the the progress of this thesis and the restart script. 
\bigskip
I would like to thank Bernhard Winkler and Markus Hilt for the great technical support regarding my questions to the \texttt{btrzx1}-cluster which helps me to develope the restart script as it is now. 
\bigskip
I would also like to thank Paul Schwanitz for his helpfulness in many situations and the good discussions in and outside academia as my best friend. In Addition to that I would like to thank Anna-Maria Pleyer, Dominik Müller and Stefan Barthelmann for the great time sharing the office together. 
\bigskip
I will also thank Anna-Maria Pleyer and my sister Cornelia Lippert for proofreading this thesis and briefcommunication which helps me to get better in spelling.
\bigskip
Outside academia, I would like to express my gratitude to my parents, my brother and his wife, my sister and Hanna Schütz for there encouragement, endurance and support during the time of this thesis.

>>>>

First of all, I would like to express my greatest gratitude to my supervisor Arthur Peeters and Florian Rath. I would like to thank both of you for your guidance and support during the submission process of the briefcommunication and the helpful hands during the the progress of this thesis and the restart script. \bigskip

I would like to thank Bernhard Winkler and Markus Hilt for the great technical support regarding my questions to the \texttt{btrzx1}-cluster which helps me to develope the restart script as it is now. \bigskip

I would also like to thank Paul Schwanitz for his helpfulness in many situations and the good discussions in and outside academia as my best friend. In Addition to that I would like to thank Anna-Maria Pleyer, Dominik Müller and Stefan Barthelmann for the great time sharing the office together. \bigskip

I will also thank Anna-Maria Pleyer and my sister Cornelia Lippert for proofreading this thesis and briefcommunication which helps me to get better in spelling. \bigskip

Outside academia, I would like to express my gratitude to my parents, my brother and his wife, my sister and my girlfriend for their encouragement, endurance and support during the time of this thesis. I know sometimes I am an workaholic and I need to be reminded outside my academic work.
